### 2016-11-09 sections/R10.03.tex
V0.03; after thesis comments

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 1: 1D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{One-Dimensional Self-Organizing Maps}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of the data. 
    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible (infinity). %Els asked what is maximum possible #
    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
    On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.

@@

        Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 (shown in Fig.~\ref{fig: regions in m31}) occupy one neuron and the other regions occupy the other one.
        The medium grey colour between two neurons indicates that there are some similarities between two groups, but they are not very similar. 
        By increasing the size of the neurons to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that region 2 separates itself from the other regions and occupies the middle neuron.
        The white colour between the two left neurons suggests that the regions which occupy these neurons are very similar to each other, while the black colour between the two right neurons indicates otherwise.

@@

        %%Network 1by14
        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network that has no neuron occupied by more than one M31 region.
        In a larger-grid SOM, the network pays more attention to smaller details and differences in the input data.
        Therefore, since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
        Regions that are located in similar areas (e.g. spiral arms, bulge, and 10 kpc ring) in M31, like regions 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to have more similarities with each other.
        In Fig.~\ref{fig: M31_net_1by14}, the right-most neuron is occupied by region 10.
        Two black colours between this region and the others indicate the large differences between this neuron and the other ones.
        Region 10 is located in the bulge of M31, and is physically separated from the other regions, which are mostly located around the inner or outer rings.
        The SOM shows that this region has completely different input values from the others: most of the values for region 10 are much higher than for the other regions, which is the main reason for its isolation.
        Region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.

    \subsection{Inside the Two Neuron Network}
        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups separates for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure*}
        \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
        \caption[Pearson correlation coefficients for data from the clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure*}

        Comparing the correlation coefficient plots for all 10 regions in M31 (Fig.~\ref{fig: cor_all}) and for the clustered data (Fig.~\ref{fig: cor_cluster1}) shows the differences between all 10 regions and clustered data and why regions 3 to 8 become separated from the other regions.
        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
        Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR, or metallicity.
        The PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.

@@

        Correlations between PAH features and SFR, and L$_\mathrm{TIR}$ are well-studied~\citep[e.g.][]{Peeters04,Tielens08}. 
        Many groups have used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Note that, since there are only 6 regions in the clustered data, even one outlier in the data may cause the correlation coefficient to become insignificant.
        Further analyses show that the absence of correlations between PAH fluxes and SFR is because of one outlier: region 6. Region 6 is located in a FUV-bright region, which breaks the correlations. 
        When we disregard this region, high correlations between 6.2 to 17.0~$\mu$m~PAHs and SFR (and L$_\mathrm{TIR}$) reappear.

        Strong anti-correlations between 6.2 to 17.0~$\mu$m~main PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all} (even if we ignore the outlier values).
        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
        First, the optical data are not corrected for dust extinction.
        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with the amount of dust due to extinction as suggested by \cite{Calzetti94}.
        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same holds for \sii~and \oiii~emission.
        Second is the possible effect of the structure of the observed regions.
        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha~emission. 
        The anti-correlations between 6.2 to 17.0~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Wu06, Gordon08,Calzetti10,Dim15}. 
        \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
        On the other hand,~\cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAH features are mostly coming from the PDRs that are surrounded by \hii~regions, and the PAH features' underlying continuum emission is from the \hii~regions.
        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.%Els: If you have an harder radiation field, you destroy your smaller PAHs. Hence, simply a harder RHI does not argue for a smaller PDRs being more plausible. 
        The latter reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.

@@

        The anti-correlation between stellar mass and PAHs could be result of the position of the regions within M31.
        Regions 5, 6, and 8 are located in the stellar disk of the galaxy and have relatively high stellar mass and faint PAH emission. 
        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in thesample that do not include an \hii~region, which could be the reason for the faint PAH emission for these regions.
        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
        Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.

>>>>

\section{One-Dimensional Self-Organizing Maps}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of exploring the M31 data with 1D maps is to monitor the general behaviour of the data. 
    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible (infinity). %Els asked what is maximum possible #
    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without clustering the data.
    On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.

@@

        Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in M31 to be divided into two groups, regions 1, 2, 9 and 10 (shown in Fig.~\ref{fig: regions in m31}) occupy one neuron and the other regions occupy the other one.
        The medium grey colour between two neurons indicates that there are some similarities between two groups, but they are not very similar. 
        By increasing the size of the neurons to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that region 2 separates itself from the other regions and occupies the middle neuron.
        The white colour between the two left neurons suggests that the regions which occupy these neurons are very similar to each other, while the black colour between the two right neurons indicates otherwise.

@@

        %%Network 1by14
        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network that has no neuron occupied by more than one M31 region.
        In a larger-grid SOM, the network pays more attention to smaller details and differences in the input data.
        Therefore, since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
        Regions that are located in similar areas (e.g. spiral arms, bulge, and 10 kpc ring) in M31, like regions 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to have more similarities with each other.
        In Fig.~\ref{fig: M31_net_1by14}, the right-most neuron is occupied by region 10.
        Two black colours between this region and the others indicate the large differences between this neuron and the other ones.
        Region 10 is located in the bulge of M31, and is physically separated from the other regions, which are mostly located around the inner or outer rings.
        The SOM shows that this region has completely different input values from the others: most of the values for region 10 are much higher than for the other regions, which is the main reason for its isolation.
        Region 8 occupies the left-most neuron in this network, suggesting that this region has the most differences from region 10.

    \subsection{Inside the Two Neuron Network}
        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups separates for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown non-linear or linear correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure*}
        \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
        \caption[Pearson correlation coefficients for data from the clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}.}
          \label{fig: cor_cluster1}
        \end{figure*}

        Comparing the correlation coefficient plots for all 10 regions in M31 (Fig.~\ref{fig: cor_all}) and for the clustered data (Fig.~\ref{fig: cor_cluster1}) shows the differences between all 10 regions and clustered data and why regions 3 to 8 become separated from the other regions.
        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halphadot, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
        Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR, or metallicity.
        The PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.

@@

        Correlations between PAH features and SFR, and L$_\mathrm{TIR}$ are well-studied~\citep[e.g.][]{Peeters04,Tielens08}. 
        Many groups have used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction-corrected \halpha \citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Note that, since there are only 6 regions in the clustered data, even one outlier in the data may cause the correlation coefficient to become insignificant.
        Further analyses show that the absence of correlations between PAH fluxes and SFR is because of one outlier: region 6. Region 6 is located in a FUV-bright region, which breaks the correlations. 
        When we disregard this region, high correlations between 6.2 to 17.0~$\mu$m~PAHs and SFR (and L$_\mathrm{TIR}$) reappear.

        Strong anti-correlations between 6.2 to 17.0~$\mu$m~main PAH features and RHI, stellar mass, \halphadot, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all} (even if we ignore the outlier values).
        Anti-correlations between PAH features and the \halphadot, \sii, and \oiii~emission could be the result of one of the following. 
        First, the optical data are not corrected for dust extinction.
        The PAH features correlate with the amount of dust while \halpha emission anti-correlates with the amount of dust due to extinction as suggested by \cite{Calzetti94}.
        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha emission, and the same holds for \sii~and \oiii~emission.
        Second is the possible effect of the structure of the observed regions.
        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha emission. 
        The anti-correlations between 6.2 to 17.0~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Wu06, Gordon08,Calzetti10,Dim15}. 
        \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
        On the other hand,~\cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAH features are mostly coming from the PDRs that are surrounded by \hii~regions, and the PAH features' underlying continuum emission is from the \hii~regions.
        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.%Els: If you have an harder radiation field, you destroy your smaller PAHs. Hence, simply a harder RHI does not argue for a smaller PDRs being more plausible. 
        The latter reason, which could also describe the anti-correlation between PAH features and \halpha emission, seems to be the more probable one.

@@

        The anti-correlation between stellar mass and PAHs could be result of the position of the regions within M31.
        Regions 5, 6, and 8 are located in the stellar disk of the galaxy and have relatively high stellar mass and faint PAH emission. 
        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in the sample that do not include an \hii~region, which could be the reason for the faint PAH emission for these regions.
        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
        Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.

### 2016-11-09 sections/R20.03.tex
V0.03; after thesis comments

 %----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 2: 2D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Two-Dimensional Self-Organizing Maps}
 \label{sec: 2d_cluster}
    Although 1D networks are helpful to give a general idea about the data, neurons in 1D maps have a maximum of two neighbours, which can limit the usefulness of the results.
    In 2D networks, each neuron has two to six neighbours, which allows them to capture a complete picture of the complicated relations in the input data.
    Accordingly, we created $10\times10$ 2D networks to study the data in detail.
    As mentioned in previous sections, the sizes of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.

    In this section we chose $10\times10$ size despite knowing, from the size of our input data, that most of the neurons would be empty.
    Using 2D networks, we are mostly interested in the ability of the SOMs to show the underlying structure of the data rather than its clustering features.
    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of the M31 data.
    Similar to Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
    \import{../sections/image_texts/}{all.tex}

    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with a very bright colour between their neurons, indicating that these two regions are very similar.
    Considering the position of these two regions in M31 (both right on the edge of the star forming rings in the galaxy), similarity of these two regions was predictable.
    The position of region 3 on the SOM is close to the position of regions 4 and 7, but with a darker colour between the nodes. 
    In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is physically closer to regions 4 and 7 than to any other region, but it is on the outer side of the star forming ring.
    Regions 5 and 6 are in the second neighbourhood (there are two neurons between them) of the SOM, with a medium gray colour between them.
    These two regions are physically located around the inner ring of the galaxy.
    Regions 8 and 6 are both in the inner ring of M31, but region 6's location has more star formation, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.

    Regions 1 and 9 are close to each other and in the same side of the star forming ring. 
    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, which might be the reason for their distances in the SOM.
    Region 2 is more distant from other regions in the galaxy and located in the star forming ring.
    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha~emission.
    Therefore, the place of region 2 in the SOM tends towards regions 1 and 4. 
    Region 10 is in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.

@@

            For analysing subsets, we create SOMs by using only PAH data, as well as using all data except the PAHs (Fig.~\ref{fig: PAHS_or_not_PAHs}).
             \import{../sections/image_texts/}{PAHS_or_not_PAHs.tex}
            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs} shows that the general position of regions in those networks are the same. 
            Region 10 is in one corner of all three networks.
            However, in Fig.~\ref{fig: all_derived_ones} and Fig.~\ref{fig: wt_pahs}, region 10 is isolated from the other regions, while in Fig.~\ref{fig: only_pahs}, region 10 is much less isolated and only shows complete dissimilarity with region 8.
            Regions 9 and 10 are totally isolated in the SOMs in Fig.~\ref{fig: wt_pahs}, but in Fig.~\ref{fig: only_pahs}, they are more similar to other regions.
            In both SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, there are dissimilarities between regions in M31 but in Fig.~\ref{fig: wt_pahs}, the colours are much darker than the ones in Fig.~\ref{fig: only_pahs}.
            This indicates that there is more similarity between the PAH features over all 10 regions than between the other input data.

            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH-only data) gradually, by adding other quantities to the input data. 
            The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e. the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha~emission and \sii~ continuum, and so on. 
            \import{../sections/image_texts/}{col3byall.tex}

@@

            Comparing Figs.~\ref{fig: col3and11_dist} to~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
            Increasing the dimension of the input data makes region 10 more isolated.
            The relative positions of regions 4 and 7 stay the same with increasing the dimensions of the input data. 
            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ does not have any obvious effect on the networks.
            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revokes those changes.

@@

            The results from Table~\ref{tab: subset1} are used to create the network in Fig.~\ref{fig: subset1}. 
            In this SOM, compared with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
            Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
            Since the difference in the amount of stellar mass was one of the most distinct differences between these three regions, removing stellar mass from the input data reduced the distance between these regions.
            Regions 5, 6 and 8 have the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they are all closer to the position of region 10.
            The distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.

@@

            Subsets, as studied in this section, can be used to learn about the effect of each input on the SOM and tell us about variation in the input data.
            Comparing Fig.~\ref{fig: only_pahs} with other networks show us that PAH features are less variable than other input data.
            These result is consistent with results from~\cite{Draine14}, who showed that the amount of PAHs in M31 for regions within 20~kpc radius is constant.
            Additional evidence for the PAH features varying significantly less than other parameters is that changing from the PAH single band emission to total PAHs does not affect the networks.
            In contrary, PACS~100~$\mu$m, stellar mass, total gas mass and RHI
            are the data with the most variance; adding them to input data increases the dark colours between neurons significantly.
            Although with changing input parameters for each network the distances between neurons and positions of the regions change, the general positions of the regions relative to one another does not change dramatically.
            Therefore, the networks created by subsets can be used to predict the properties of unobserved quantities in other regions of the galaxy.
            For example, photometry data, stellar mass, SFR, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, and dust mass are available for most of M31. 
            The network from Fig.~\ref{fig: wt_pahs} can be applied to 
            these data from another region in M31.
            By comparing the position of the new region with respect to our original 10 regions in the network, one would have an estimate for total PAHs in the new region without having any observational data for it.

@@

    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, can yield ideas about data entry from other regions/galaxies.
    In this section we showed that we can use networks that are created by data from nearby galaxies to study the properties of other galaxies.
    If an SOM network is available, applying data from other regions to the network is very time efficient to learn about relative properties of galaxies.
    We should note that, since we normalized data before using them in the networks, we only see relative properties of the regions.
    Therefore, we need data from at least a few regions in the galaxy to use this application of SOMs and cannot use these networks to learn about properties of a single region in other galaxies.
    As mentioned before, since we know the properties of regions in M31, from Fig.~\ref{fig: subset9}, we can quickly conclude that region 7 and 4 have relatively higher surface brightness than the other regions in M101. 
    Similarly, we can say that regions 6 and 8 in M101 have very faint surface brightness for most of the parameters, and are very different from regions 7 and 4.

>>>>

\section{Two-Dimensional Self-Organizing Maps}
 \label{sec: 2d_cluster}
    Although 1D networks are helpful to give a general idea about the data, neurons in 1D maps have a maximum of two neighbours, which can limit the usefulness of the results.
    In 2D networks, each neuron has two to six neighbours, which allows them to capture a complete picture of the complicated relations in the input data.
    Accordingly, we created $10\times10$ 2D networks to study the data in detail.
    As mentioned in previous sections, the sizes of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.

    In this section we chose $10\times10$ size despite knowing, from the size of our input data, that most of the neurons would be empty.
    Using 2D networks, we are mostly interested in the ability of the SOMs to show the underlying structure of the data rather than its clustering features.
    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of the M31 data.
    Similar to Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
    In Fig.~\ref{fig: all_derived_ones}, all the regions except regions 4 and 7 are surrounded by white colours.
    This indicates that all the immediate neighbours for neurons occupied with each region have similar properties as the occupied ones, except for regions 4 and 7.
    These two regions are sitting in very close regions and their smallest dissimilarity causes the changes in distances between their neighbours.
    \import{../sections/image_texts/}{all.tex}

    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with a very light colour between their neurons, indicating that these two regions are very similar.
    Considering the position of these two regions in M31 (both right on the edge of the star forming rings in the galaxy), similarity of these two regions was predictable.
    The position of region 3 on the SOM is relatively close to the position of regions 4 and 7, but with a darker colour between the nodes. 
    In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is physically closer to regions 4 and 7 than to any other region, but it is on the outer side of the star forming ring.
    Regions 5 and 6 are in the second neighbourhood (there are two neurons between them) of the SOM, with a medium gray colour between them.
    These two regions are physically located around the inner ring of the galaxy.
    Regions 8 and 6 are both in the inner ring of M31, but region 6's location has more star formation, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.

    Regions 1 and 9 are close to each other and in the same side of the star forming ring. 
    However, region 1 is in an area of the galaxy with less diffuse \halpha emission than region 9, which might be the reason for their distances in the SOM.
    Region 2 is more distant from other regions in the galaxy and located in the star forming ring.
    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha emission.
    Therefore, the place of region 2 in the SOM tends towards regions 1 and 4. 
    Region 10 is in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.

@@

            For analysing subsets, we create SOMs by using only PAH data, as well as using all data except the PAHs (Fig.~\ref{fig: PAHS_or_not_PAHs}).
             \import{../sections/image_texts/}{PAHS_or_not_PAHs.tex}
            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs} shows that the general position of almost all regions in those networks are the same. 
            Region 10 is in one corner of all three networks.
            However, in Fig.~\ref{fig: all_derived_ones} and Fig.~\ref{fig: wt_pahs}, region 10 is isolated from the other regions, while in Fig.~\ref{fig: only_pahs}, region 10 is much less isolated and only shows complete dissimilarity with region 8.
            Regions 9 and 10 are totally isolated in the SOMs in Fig.~\ref{fig: wt_pahs}, but in Fig.~\ref{fig: only_pahs}, they are more similar to other regions.
            In both SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, there are dissimilarities between regions in M31 but in Fig.~\ref{fig: wt_pahs}, the colours are much darker than the ones in Fig.~\ref{fig: only_pahs}.
            This indicates that there is more similarity between the PAH features over all 10 regions than between the other input quantities.

            We increased the dimension of the input data in Fig.~\ref{fig: only_pahs} (PAH-only data) gradually, by adding other quantities to the input data. 
            The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e. the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha emission and \sii~photometry, and so on. 
            \import{../sections/image_texts/}{col3byall.tex}

@@

            Comparing Figs.~\ref{fig: col3and11_dist} to~\ref{fig: col3and25_dist} shows that adding \halpha emission data to PAH features causes regions 9 and 10 become isolated. 
            Increasing the dimension of the input data makes region 10 more isolated.
            The relative positions of regions 4 and 7 stay the same with increasing the dimensions of the input data. 
            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ does not have any obvious effect on the networks.
            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revokes those changes.

@@

            The results from Table~\ref{tab: subset1} are used to create the network in Fig.~\ref{fig: subset1}. 
            In this SOM, compared with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
            Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
            Since the difference in the amount of stellar mass was one of the most distinct differences between these three regions, removing stellar mass from the input data reduced the distance between these regions.
            Regions 5, 6 and 8 have the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they are all closer to the position of region 10.
            The distance between regions 2 and 3 is reduced but in the meantime the colour between them becomes darker.

@@

            Subsets, as studied in this section, can be used to learn about the effect of each input on the SOM and tell us about variation in the input data.
            Comparing Fig.~\ref{fig: only_pahs} with other networks show us that PAH features are less variable than other input data.
            These result is consistent with results from~\cite{Draine14}, who showed that the amount of PAHs in M31 for regions within 20~kpc radius is constant.
            Additional evidence for the PAH features varying significantly less than other parameters is that changing from the PAH single band emission to total PAHs does not affect the networks.
            In contrary, PACS~100~$\mu$m, stellar mass, total gas mass and RHI
            are the data with the most variance; adding them to input data increases the dark colours between neurons significantly.
            Although with changing input parameters for each network the distances between neurons and positions of the regions change, the general positions of the regions relative to one another does not change dramatically.
            Therefore, the networks created by subsets can be used to predict the properties of unobserved quantities in other regions of the galaxy.
            For example, photometry data, stellar mass, SFR, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, and dust mass are available for most of M31. 
            The network from Fig.~\ref{fig: wt_pahs} can be applied to 
            these data from another region in M31.
            By comparing the position of the new region (with the same spatial size of these 10 regions) with respect to our original 10 regions in the network, one would have an estimate for total PAHs in the new region without having any observational data for it.

@@

    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets} can yield ideas about data entry from other regions/galaxies.
    In this section we showed that we can use networks that are created by data from nearby galaxies to study the properties of other galaxies.
    If an SOM network is available, applying data from other regions to the network is very time efficient to learn about relative properties of galaxies.
    We should note that, since we normalized data before using them in the networks, we only see relative properties of the regions.
    Therefore, we need data from at least a few regions in the galaxy to use this application of SOMs and cannot use these networks to learn about properties of a single region in other galaxies.
    As mentioned before, since we know the properties of regions in M31, from Fig.~\ref{fig: subset9}, we can quickly conclude that regions 7 and 4 have relatively higher surface brightness than the other regions in M101. 
    Similarly, we can say that regions 6 and 8 in M101 have very faint surface brightnesses in most of the parameters, and are very different from regions 7 and 4.
